A Transactional Memory System for Parallel Python

### 2014-07-29 talk/dls2014/paper/paper.tex
clarifications

Note, since the above configuration is specified at compile time,
all these areas are at offsets inside the segments known to the
compiler. This makes some checks very efficient, e.g.\ checking
if an object resides in the nursery only requires comparing its $SO$
to the static boundaries of the nursery.

@@

@@

We performed all benchmarks on a machine with an Intel Core i7-4770
CPU~@3.40GHz (4 cores, 8 threads).  There are 16~GiB of memory
available and we ran them under Ubuntu 14.04 with a Linux 3.13.0
kernel. The STM system was compiled with a number of segments $N=4$
and a maximum amount of memory of 1.5~GiB (both are configurable at
compile time).

>>>>

Note, since the above configuration is currently specified at compile time,
all these areas are at offsets inside the segments known to the
compiler. This makes some checks very efficient, e.g.\ checking
if an object resides in the nursery only requires comparing its $SO$
to the static boundaries of the nursery. It is possible that we want
some parameters to be configurable at startup or even during the
runtime. In that case we can still use a compile-time specified
maximum so that these checks are still efficient. E.g.\ limiting the
maximum amount of memory available to the application statically to a few
terabytes is fine because it corresponds to virtual memory,
the real physical memory is assigned on-demand by the operating
system.

@@

Note, this works well for interpreters that really allocate things
all the time. In the presence of an optimising just-in-time compiler,
some loops may indeed not allocate anything and therefore still need
the insertion of a safe-point check.

@@

We performed all benchmarks on a machine with an Intel Core i7-4770
CPU~@3.40GHz (4 cores, 8 threads) with disabled Hyper-Threading and
Turbo Boost for less variation in the results.  There are 16~GiB of memory
available and we ran them under Ubuntu 14.04 with a Linux 3.13.0
kernel. The STM system was compiled with a number of segments $N=4$
and a maximum amount of memory of 1.5~GiB (both are configurable at
compile time).
